Semantic Holographic Memories

### 2016-06-24 papers/hrr-paper/paper.tex
Added Captions to Scalar Encoder graphics in hrr-paper. Added experiment for max number of correct bindings added on top of each other in hrr.

\begin{figure}
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{img/scalar-pre-perm-fft.png}
\caption{Scalar}
\label{fft-a}
\end{subfigure}
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{img/scalar-random-fft.png}
\caption{Random}
\label{fft-b}
\end{subfigure}
\caption{.}
\label{fft}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{img/scalar-perm-step-fft.png}
\caption{.}
\label{perm-fft}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{img/scalar-post-perm.png}
\caption{Binging}
\label{perm-a}
\end{subfigure}
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{img/scalar-post-perm-probe.png}
\caption{Probing}
\label{perm-b}
\end{subfigure}
\caption{.}
\label{perm}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\columnwidth]{img/scalar-pre-perm-fft.png}
\includegraphics[width=\columnwidth]{img/scalar-random-fft.png}
\caption{Fourier space conversions of a Gaussian bell and a random vector.}
\label{fft}
\end{figure}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{img/scalar-perm-step-fft.png}
\caption{Plots on the effect of permuting a Gaussian bell, and the impact on Fourier space.}
\label{perm-fft}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{img/scalar-post-perm.png}
\caption{Binging}
\label{perm-a}
\end{subfigure}
\begin{subfigure}{1\columnwidth}
\includegraphics[width=\columnwidth]{img/scalar-post-perm-probe.png}
\caption{Probing}
\label{perm-b}
\end{subfigure}
\caption{Figure \ref{perm-a} shows the binding of the permuted Gaussian for value 8 on a scale to 10 with the symbolic representation of "ball", which is random. In figure \ref{perm-b} "ball" is being probed, and the expected result is a Gaussian bell for 8, mixed with some noise.}
\label{perm}
\end{figure}
